Exploring Potential 6LoWPAN Traffic Side Channels

### 2017-04-06 Writing/iotprotocols.tex
Update

%Avaible security options.
For our settings, there are two schemes available for packet encryption, namely 802.15.4 Security\cite{802154} and DTLS\cite{rfc6347}. 802.15.4 Security is provided by noncoresec\cite{noncoresec} which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network. tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively. We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously as the resulting packets exceeded the 802.15.4 MTU\footnote{Maximum Transmission Unit.} and thus not practical.

>>>>

%Avaible security options.
For our settings, there are two schemes available for packet encryption, namely 802.15.4 Security\cite{802154} and DTLS\cite{rfc6347}. 802.15.4 Security is provided by noncoresec\cite{noncoresec} which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network. tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively. We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously, as the de facto encryption schemes are both AES-128 CCM*. Overlapping them does not enhance the security but only increases the overhead.
